The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-03-26 SC-challenge.tex
extended acknowledgements
revised table a bit

Key challenges and research directions (with possible solutions/methods) are shown in Table~\ref{tab:challenges}.

@@

Identify necessary metadata associated with software for citation & The CodeMeta project~\cite{CodeMeta} is working to do this now \\

Standardize proper formats for citing software in publications & The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group to implement the software citation principles will likely start, and part of the charge for this group will be to work with publishers on this challenge \\

Establish mechanisms for software to cite other software (i.e., dependencies) & Software publication as software papers will allow this.  For software that is directly published, this is an open challenge with no clear path forward \\

@@

Increase cultural acceptance of the concept of software as a digital product & Will happen over time; unclear how to accelarate \\ 
\bottomrule
\end{tabular}}
\end{table}

\knnote{suggest ``few possible answers or clear path that might be followed''}

@@

 Acknowledgments
\begin{acks}
The authors wish to thank the members of the SciSIP community and mailing list, in particular Chris Belter, James Howison, and Joshua Rosenbloom, for a useful discussion on incentives for software publications and how their impact has and could further be measured.
\end{acks}

>>>>

Key challenges and research directions (with possible solutions\slash methods) are shown in Table~\ref{tab:challenges}.

@@

Identify necessary metadata associated with software for citation & 
We suggest metadata below, and the CodeMeta project~\cite{CodeMeta} is working to determine minimal metadata \\

Standardize proper formats for citing software in publications & 
The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group will initiate implementation activities. Part of the charge for this group will be to work with publishers on this challenge \\

Establish mechanisms for software to cite other software (i.e., dependencies) & 
Software publication as software papers allows this. For software that is directly published, this is an open challenge with no obvious path forward \\

@@

Increase cultural acceptance of the concept of software as a digital product & 
Acceptance will happen over time; unclear how to accelerate \\ 
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{acks}
The authors wish to thank the members of the SciSIP community and mailing list, in particular Chris Belter, James Howison, and Joshua Rosenbloom, for a useful discussion on incentives for software publications and how their impact has and could further be measured.
In addition, the authors acknowledge members of the FORCE11 Software Citation Working Group, whose views contributed to this document.
\end{acks}
